Amazon in Presidential Speeches in Brazil: data exploration for contexts

### 2021-10-28 data_exploration_2_context.Rmd
More updates to data exploration markdown

```{r}
# Location was added with poldis::extraxt_location(), still needs to be improved...
summary(as.factor(Amazon_speeches$location))

@@

```{r narratives}
# Amazon_speeches <- dplyr::mutate(Amazon_speeches, narrative = case_when(grepl("", text) ~ "", grepl("", text) ~ "", grepl("", text) ~ ""))
# summary(as.factor(Amazon_lc$narrative))
```

>>>>

```{r location, warning=FALSE, message=FALSE}
# Location was added with poldis::extraxt_location(), still needs to be improved...
summary(as.factor(Amazon_speeches$location))

@@

```{r narratives, warning=FALSE, message=FALSE}
# Amazon_speeches <- dplyr::mutate(Amazon_speeches, narrative = case_when(grepl("", text) ~ "", grepl("", text) ~ "", grepl("", text) ~ ""))
# summary(as.factor(Amazon_lc$narrative))
```
